---
title: "trying to scrape indeed with RSelenium"
author: "Jack Wright"
date: "10/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Getting started
Download Docker
https://www.docker.com/products/docker-desktop

Docker
-container for the Rselenium server to live in 
-go through tutorial inside docker

RSelenium

-install.packages("RSelenium")

Optional
-install browser extension "selectorgadget"
https://selectorgadget.com/





Setting up server in command line
                 
docker run -d -p 4445:4444 selenium/standalone-chrome


## connecting to RSelenium Server

```{r}
library(RSelenium)
remDr <- remoteDriver(
  remoteServerAddr = "localhost",
  port = 4455L, #whatever port number you picked
  browserName = "chrome"
)
remDr$open()


```


Navigate to indeed "data science" "new york"

-we could look over multiple cities or multiple search terms

```{r}
remDr$navigate("https://www.indeed.com/jobs?q=data+science&l=New+York")
remDr$maxWindowSize()
remDr$refresh()
remDr$screenshot(display=TRUE)

```

#trying to search for "clickcards"

```{r}
webElems<-remDr$findElements(using="css",value=".clickcard")
clickcard_info<-unlist(lapply(webElems,function(x){x$getElementText()}))
clickcard_info
```


## sending event to element

```{r}

webElems<-remDr$findElements(using = "css selector",".jobtitle")

resTitles<-unlist(lapply(webElems,function(x){x$getElementText()}))

resTitles

```

#want to click the first link

(works up until the click)

```{r}



#move mouse to element selected

remDr$mouseMoveToLocation( webElement=webElems[[1]])

remDr$click()

#frame is opened for the job
remDr$maxWindowSize()
remDr$screenshot(display=TRUE)

webElems<-remDr$findElements(using="tag name","iframe")


#pulls link for job posting's own page
sapply(webElems,function(x){x$getElementAttribute("src")})

remDr$switchToFrame(webElems[[1]])
#XML::htmlParse(remDr$getPageSource()[[1]])

insideElems<-remDr$findElements(using="id",value = "jobDescriptionText")
jdescription<-sapply(insideElems,function(x){x$getElementText()})

jdescription

```



```{r}


```

